The Changing Face of Pediatric Pulmonary Exacerbations in CF (NACFC 2023)

### 2023-03-29 Scott Sagel/PEx in CF/nacfc_2023.qmd
Update nacfc_2023.qmd

---
title: "Changing face of pediatric pulmonary exacerbations in CF"
author: "Tim Vigers"
date: "today"
format:
  html:
    toc: false
    code-fold: true
    self-contained: true
    fig-cap-location: top
    page-layout: full
editor: source
execute: 
  echo: false
---

>>>>

---
title: "The Changing Face of Pediatric Pulmonary Exacerbations in CF (NACFC 2023)"
author: "Tim Vigers"
date: "today"
format:
  html:
    toc: false
    code-fold: true
    self-contained: true
    fig-cap-location: top
    page-layout: full
editor: source
execute: 
  echo: false
---
